### 2020-01-03 text/suppl_methods.Rmd

---
author: "N.S."
date: "15 October 2019"
output: html_document
---

# Supplementary methods
## 1. Underwater visual census database
\noindent We used a published global database of field data collection of belt transects [@Barneche2019]. This database encompasses transect data across 585 sites in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, Western Atlantic (Figure). This database only includes sites with a hard reef bottom are at the outer reef slope and were carried out at a constant depth, parallel to the reef crest. We splected the species inside families for which we have body stoichiometric data, that were at least 7cm to minimize bias and finally, we discarded rare species, for which less than 20 individuals were ever recorded across all sites. The dataset then included 1110 species of 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).

## Phylogeny

## 2. Parameter estimates

### 2.1. Growth parameters

#### Data compilation
We first compiled maximum lengths for all species with FishBase and used these lengths for the $l_{\infty}$ (REF). For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were to be equal to  equal to its maximum length [i.e. $k_{max}$, @Morais2019]. $t0$ was kept constant at 0 for all species.

@@

#### Statistical analysis and extrapolation

@@

\begin{equation}
	\textrm{ln}kmax = (\beta_\textrm{0} + \gamma_\textrm{0phy}) +  \beta_\textrm{1} \textrm{ln}size +  \beta_\textrm{2} sst + \epsilon,
	\label{kmax}
\end{equation}

\noindent where $\textrm{ln}kmax$ represents the natural log-transformed kmax value, $\beta_\textrm{0}$ is the fixed-effect intercept, $\gamma_\textrm{0phy}$ is the vector of random-effect coefficients that account for the resisual intercept variation, based on the relatedness as described by the phylogeny, $\beta_\textrm{1}$ is the slope for the natural transformed maximum body size, $\beta_\textrm{2}$ is the slope for the average ambient sea surface temperature, $\epsilon$ is the residual variation.
\noindent We used uninformative priors and ran the model for 2000 iterations with a warm-up of 1000 iteration for 4 chains. 
\noindent The model fit confirmed a negative relationship of $\textrm{ln}kmax$ with $\textrm{ln}size$, and a positive relationship with sea surface temperature. The Bayesian R2 of the model was 0.73759 (95%CI: 0.702-0.769). 
\noindent The phylogenetic heritability (equivalent to Pagel’$\lambda$ (REF)) was estimated as the proportion of total variance, conditioned on the effects, attributable to the  phylogeny(i.e. $\lambda = (\textrm{sd}(\gamma_\textrm{0phy})^2  / (\textrm{sd}(\gamma_\textrm{0phy})^2 + \epsilon^2)$). This calculation resulted in a phylogenetic signal of 0.74 (95% CI: 0.70 - 0.77).

@@

Group-Level Effects: 
~phylo (Number of levels: 181) 
              Estimate Est.Error l-95% CI u-95% CI Eff.Sample Rhat
sd(Intercept)     0.83      0.09     0.67     1.01        843 1.00

Population-Level Effects: 
           Estimate Est.Error l-95% CI u-95% CI Eff.Sample Rhat
Intercept      0.66      0.58    -0.48     1.81       1498 1.00
logsizemax    -0.76      0.10    -0.96    -0.57       1281 1.00
sstmean        0.02      0.01    -0.00     0.05       4071 1.00

Family Specific Parameters: 
      Estimate Est.Error l-95% CI u-95% CI Eff.Sample Rhat
sigma     0.46      0.02     0.43     0.50       1991 1.00

@@

### 2. Body stoichiometry
#### 3.1 Data collection

#### 3.2 Data analysis

only species with nrep >= 3

Stoichiometry is well conserved within taxonomic entities. Through a database of 1633 individuals, 108 species, locations: Moorea, Palmyra, Carribean

25 families
 [1] "Acanthuridae"   "Balistidae"     "Bothidae"       "Chaetodontidae" "Cirrhitidae"    "Fistulariidae" 
 [7] "Haemulidae"     "Holocentridae"  "Kyphosidae"     "Labridae"       "Lethrinidae"    "Lutjanidae"    
[13] "Monacanthidae"  "Mugilidae"      "Mullidae"       "Ostraciidae"    "Pempheridae"    "Pomacanthidae" 
[19] "Pomacentridae"  "Sciaenidae"     "Scorpaenidae"   "Serranidae"     "Siganidae"      "Tetraodontidae"
[25] "Zanclidae"

multivariate model

extrapolation

phylopars from rphylopars
for each iteration of 1 chain, for each tree of 100 trees

### 3. Diet

>>>>

---
output:
  pdf_document: default
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Supplementary methods
# 1. Underwater visual census database
\noindent We used a published global database of field data collection of belt transects [@Barneche2019]. This database encompasses transect data across 585 sites in the Central Indo-Pacific, Central Pacific, Eastern Pacific, Western Indian, Eastern Atlantic, Western Atlantic (Figure). This database only includes sites with a hard reef bottom are at the outer reef slope and were carried out at a constant depth, parallel to the reef crest. We splected the species inside families for which we have body stoichiometric data, that were at least 7cm to minimize bias and finally, we discarded rare species, for which less than 20 individuals were ever recorded across all sites. The dataset then included 1110 species of 25 families (Acanthuridae, Balistidae, Bothidae, Chaetodontidae, Cirrhitidae, Fistulariidae, Haemulidae, Holocentridae, Kyphosidae, Labridae, Lethrinidae, Lutjanidae, Monacanthidae, Mugilidae, Mullidae, Ostraciidae, Pempheridae, Pomacanthidae, Pomacentridae, Sciaenidae, Scorpaenidae, Serranidae, Siganidae, Tetraodontidae, Zanclidae).

# 2. Phylogeny

# 3. Parameter estimates

\newpage

\begin{table}[h!]
\centering
\caption{. Overview of model input parameters. VBGC = von Bertalanffy growth curve.}
\begin{tabular}{l l l}
\hline
\rowcolor{lightgrey}
Symbol & Description & Unit\\
\hline
$k$ & Index for element C, N or P & \_ \\
$a_\textrm{k}$  & Element-specific assimilation efficiency & \% \\
$l_\textrm{t}$  & Total length of individual at time t & cm \\
$l_{\infty}$  & Asymptotic adult length (VBGC) & cm \\
$\kappa$  & Growth rate parameter (VBGC) & $\textrm{yr}^{-1}$ \\
$t_0$  & Age at settlement (VBGC) & $\textrm{yr}$ \\
$lw_a$  & Parameter length-weight relationship & $\textrm{g cm}^{-1}$ \\
$lw_b$  & Parameter length-weight relationship & \_\\
$Q_\textrm{k}$  & Element-specific body content percentage of dry mass & \% \\
$f_\textrm{0}$  & Metabolic normalisation constant independent of body mass & $\textrm{g C} \textrm{g}^{-\alpha} \textrm{d}^{-1}$ \\
$\alpha$  & Mass-scaling exponent &  \_\\
$\theta$  & Activity scope & \_ \\
$v$  & Environmental temperature & \textdegree C \\
$h$  & trophic level & \_ \\
$r$  & Aspect ratio of caudal fin & \_ \\
$F_\textrm{0Nz}$  & Mass-specific turnover rate of N & $\textrm{g N} \textrm{g}^{-1} \textrm{d}^{-1}$ \\
$F_\textrm{0Pz}$  & Mass-specific turnover rate of P & $\textrm{g P} \textrm{g}^{-1} \textrm{d}^{-1}$ \\
$D_\textrm{k}$  & Elemental stoichiometry of diet & \% \\
\hline
\end{tabular}
\end{table}

\newpage

## 3.1. Growth parameters

### 3.1.1 Data compilation
We first compiled maximum lengths for all species with FishBase and used these lengths for the $l_{\infty}$ (REF). For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were to be equal to  equal to its maximum length [i.e. $k_{max}$, @Morais2019]. $t0$ was kept constant at 0 for all species.

@@

### 3.1.2 Statistical analysis and extrapolation

@@

\begin{equation}
	\textrm{ln}kmax = (\beta_\textrm{0} + \gamma_\textrm{0phy}) +  \beta_\textrm{1} \textrm{ln}sizemax +  \beta_\textrm{2} sst + \epsilon,
	\label{kmax}
\end{equation}

\noindent where $\textrm{ln}kmax$ represents the natural log-transformed kmax value, $\beta_\textrm{0}$ is the fixed-effect intercept, $\gamma_\textrm{0phy}$ is the vector of random-effect coefficients that account for the resisual intercept variation, based on the relatedness as described by the phylogeny, $\beta_\textrm{1}$ is the slope for the natural transformed maximum body size, $\beta_\textrm{2}$ is the slope for the average ambient sea surface temperature, $\epsilon$ is the residual variation.
\noindent We used uninformative priors and ran the model for 2000 iterations with a warm-up of 1000 iteration for 4 chains. 
\noindent The model fit confirmed a negative relationship of $\textrm{ln}kmax$ with $\textrm{ln}size$, and a positive relationship with sea surface temperature. The Bayesian R2 of the model was 0.73759 (95\%CI: 0.702-0.769). 
\noindent The phylogenetic heritability (equivalent to Pagel’$\lambda$) was estimated as the proportion of total variance, conditioned on the effects, attributable to the  phylogeny(i.e. $\lambda = (\textrm{sd}(\gamma_\textrm{0phy})^2  / (\textrm{sd}(\gamma_\textrm{0phy})^2 + \epsilon^2)$). This calculation resulted in a phylogenetic signal of 0.74 (95\% CI: 0.70 - 0.77).

@@

Group-Level Effects: 
~phylo (Number of levels: 181) 
              Estimate Est.Error l-95\% CI u-95\% CI Eff.Sample Rhat
sd(Intercept)     0.83      0.09     0.67     1.01        843 1.00

Population-Level Effects: 
           Estimate Est.Error l-95\% CI u-95\% CI Eff.Sample Rhat
Intercept      0.66      0.58    -0.48     1.81       1498 1.00
logsizemax    -0.76      0.10    -0.96    -0.57       1281 1.00
sstmean        0.02      0.01    -0.00     0.05       4071 1.00

Family Specific Parameters: 
      Estimate Est.Error l-95\% CI u-95\% CI Eff.Sample Rhat
sigma     0.46      0.02     0.43     0.50       1991 1.00

@@

## 3.2 Body stoichiometry    
### 3.2.1 Data collection    
\noindent 1633 individuals of 108 species and 25 families were collected between 2015 and 2017 in Moorea, Carribean and Palmyra. Their gut contents were removed, and the whole body was freeze-dried and ground to powder with a Precellys homogeniser. $Q_\textrm{k}$ (\%) were then measured in the lab using standard methods. Ground samples were analysed for \%C and \%N content using a CHN Carlo-Erba elemental analyzer (NA1500) for \%P using dry oxidation-acid hydrolysis extraction followed by a colorimetric analysis (Allen et al. 1974). Elemental content was calculated based on dry mass.

### 3.2.2 Data analysis and extrapolation

\noindent We fitted C, N and P contents (\%) through a hierarchical phylogenetic multivariate normal model with phylogenetic effects and random effects per species.

\begin{equation}
	\begin{bmatrix}Y_1 \\ Y_2 \\ Y_3\end{bmatrix} \sim MVNormal(\begin{bmatrix}mu1 \\ mu2 \\ mu3\end{bmatrix}, S),
	\label{cnp}
\end{equation}

\begin{equation}
	mu_{\textrm{n}\times\textrm{k}} = \beta_\textrm{0 k} + \gamma_{\textrm{0phy}\times\textrm{k}} + \gamma_{\textrm{0sp}\times\textrm{k}},
	\label{cnp2}
\end{equation}

\noindent where $Y_1$, $Y_2$ and $Y_3$ are the \% content of $\textrm{C}$, $\textrm{N}$, and $\textrm{P}$ respectively,   $mu_{\textrm{n}\times\textrm{k}}$ represents the average \% content of element $k$ ($\textrm{C}$, $\textrm{N}$, and $\textrm{P}$) per species, $\beta_\textrm{0 k}$ is the fixed-effect intercept for each element $k$, $\gamma_{\textrm{0phy}\times\textrm{k}}$ is the matrix of random-effect coefficients that account for the intercept variation, based on the relatedness as described by the phylogeny per element k, $\gamma_{\textrm{0sp}\times\textrm{k}}$ is the matrix of random-effect coefficients that account for the residual species-level intercept variation per element k.

\noindent We used uninformative priors and ran the model for 2000 iterations with a warm-up of 1000 iteration for 4 chains. 
\noindent The Bayesian R2 of the model was 0.39 (95\%CI: 0.36-0.42), 0.50 (95\%CI: 0.48-0.53), and 0.43 (95\%CI: 0.40-0.46) for C, N and P respectively. 
\noindent The phylogenetic heritability was 0.41 (95\%CI: 0.28-0.55), 0.58 (95\%CI: 0.4-0.66), and 0.57 (95\%CI: 0.46-0.69) for C, N, and P respectively.

\noindent As before, we used 1000 fitted draws for each species, and 100 phylogenetic trees to extrapolate to all species with unknown body stoichiometry. Specifically, we used the phylopars function from the Rphylopars package [@Bruggeman2009]. This function uses ancectral state reconstruction and brownian motion, and takes the correlation between C, N and P into account.

## 3.3 Diet stoichiometry    
### 3.3.1 Data collection 
\noindent We collected 345 adult individuals of 37 species and 12 families between 2018 and 2019 in Mo'orea and Tetiaroa, two Polynesian islands. We extracted the stomach content and stored it in a 2ml tube. After freezing the samples, we dry-froze all samples for at least 24 hours, and ground to powder. Then, samples were sent to the lab (more info!!) for CNP% content analysis.

### 3.3.2 Data analysis and extrapolation  
\noindent We extracted trophic group information from ref diet paper. We constructed a simple multivariate Bayesian regression model to summarize CNP\% content data per trophic group with a random effect at the species level. This model had a Bayesian R2 of 0.61 (0.56-0.65), 0.31 (0.23-0.38), and 0.48 (0.42-0.54).           
bayes_R2(fit_cnpdiet)
     Estimate  Est.Error      Q2.5     Q97.5
R2c 0.6250538 0.02299497 0.5756378 0.6642792
R2n 0.3043510 0.03973636 0.2271046 0.3771861
R2p 0.4857449 0.03164611 0.4191740 0.5417580

\noindent We then predicted the CNP\% per diet category.

   cat    Dc_m  Dn_m  Dp_m Dc_sd Dn_sd Dp_sd
  <chr> <dbl> <dbl> <dbl> <dbl> <dbl> <dbl>
1 1      30.6  4.13 0.424  2.88 0.865 0.197
2 2      35.1  7.96 1.50   2.71 0.857 0.193
3 3      33.1  5.79 0.751  3.52 1.06  0.242
4 4      38.1  7.45 0.879  5.14 1.60  0.360
5 5      28.9  5.10 0.619  3.35 1.03  0.239

## 3.4 Metabolic parameters    
### 3.4.1 Data collection
